### 2016-07-04 case-studies.tex
edits

In this section, we present two case studies that demonstrate the
applicability of our framework in varied settings, and its consequent
practical utility. Both our case studies target Ruby-on-Rails
applications. To analyze these, and other similar open-source
applications, we have developed a symbolic execution engine that
compiles a Rails program to an abstract program in an extended version
of \txnimp, along with some proof automation support.\footnote{Details
  ( can be found in the supplementary material.  Source code for our
  implementation, along with applications and experiments, are
  available at the following anonymized url: \url{...}} The focus of
our formal verification efforts are such translated \txnimp programs.

>>>>

In this section, we present two case studies that demonstrate the
applicability of our framework in varied settings, and its consequent
practical utility. Both our case studies target Ruby-on-Rails
applications. To analyze these, and other similar open-source
applications, we have developed a symbolic execution engine that
compiles a Rails program to an abstract program in an extended version
of \txnimp, along with some proof automation support.\footnote{Details
   can be found in the supplementary material.  Source code for our
  implementation, along with applications and experiments, are
  available at the following anonymized url: \url{...}} The focus of
our formal verification efforts are such translated \txnimp programs.
